---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# dpcc

<!-- badges: start -->
<!-- badges: end -->

`dpcc` aims to enable fast computation and path visualization of L1 convex clustering
with identical weights. 

## Installation

You can install `dpcc` from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("dpcc")
devtools::install_github("bingyuan-zhang/dpcc")
```

Load the packages.
```{r}
library(dpcc)
```

## Example
We first generate the three clusters example.
```{r}
#install.packages("ggplot2")
library(ggplot2)
set.seed(12)
n = 50
error = matrix(rnorm(n*2,sd = 1.4),n,2)
which=sample(1:3, n, replace=TRUE)
xmean = matrix(rnorm(3*2,sd = 11),3,2)
tb1 = error + xmean[which,]
data = data.frame(
  x = scale(tb1[,1]),
  y = scale(tb1[,2]),
  clusters = factor(which)
)

ggplot(data,aes(x,y,color=factor(clusters))) + 
  geom_point(size = 2, show.legend = FALSE)
```
Now we construct a sequence of tuning parameters with length K = 10.
```{r}
dat = data.matrix(data)[,1:2]
lam_max = find_lambda(dat)/1.5; 
K = 10
Lam = sapply(1:K, function(i) i/K*lam_max) 

Lam
```

Next we use the function in the package to draw the clusterpath.
```{r}
res = cpaint(dat,Lam)
df.paths <- data.frame(x = dat[,1],y = dat[,2], group=1:n)
for (j in 1:K) {
  df <- data.frame(x=res[[1]][j,], y=res[[2]][j,], group=1:n)
  df.paths <- rbind(df.paths,df)
}

ggplot(data) + 
  geom_path(data = df.paths, aes(x = x, y = y, group=group), colour='grey60', alpha = 0.5) +
  geom_point(aes(x = x, y = y, col = clusters), size = 2, show.legend = FALSE)
```

References
--------
[1.] [Dynamic visualization for L1 fusion convex clustering in near-linear time] 
Bingyuan Zhang, Yoshikazu Terada, Jie Chen (UAI 2021 to appear).


